High-Dim Project

### 2014-12-19 highdim-paper/paper.tex
added the missing image

\begin{algorithm}
  \For{$i \gets 0, \ldots, rows(Z) $}{
	   Get the indices of the N largest columns from row i\\
       Output these indices to a new group\\
       Mark all cell in these columns in the matrix Z to be 0.\\
  }
\end{algorithm}

>>>>

\begin{algorithm}
  \For{$i \gets 0, \ldots, rows(Z) $}{
	   Get the indices of the N largest columns from row i\\
       Output these indices to a new group\\
       Mark all cells in these columns in the matrix Z to be 0.\\
  }
\end{algorithm}
